---
output: html_document
---
color.terminal.branches - Color only the terminal branches of a phylogeny by the corresponding trait value
========================================================

The code for this function can be found here. The function has the potential to take many arguments:

* `phy` - Object of class `phylo`
* `data` - Named numeric vector, where the names match the tip labels in `phy`
* `breaks` - Numeric vetor of length 1 determining how many times to partition `data`
* `cols` - Character vector specifying the colors to be used in creating the color palette. See [colorRamp](http://www.inside-r.org/r-doc/grDevices/colorRampPalette) for more information
* `non.terminal.col` - Character vector of length 1, the color for the non-terminal branches in the phylogeny
* `edge.width` - Numeric vector of length 1. The thickness of the following ape's [plot.phylo](http://www.inside-r.org/packages/cran/ape/docs/plot.phylo)
* `col.bias` - Numeric vector of length 1. A higher value will produce more widely spaced colors at higher trait values, see [colorRamp](http://www.inside-r.org/r-doc/grDevices/colorRampPalette) for more information
* `legend.title` - Character vector specifying the title for the legend
* `show.tip.label` - Logical. Show the tip labels of the phylogeny?

To demonstrate some functionality, we first need to simulate some phylogenetic and trait data
```{r}
library(ape)

phy <- read.nexus("example_phylogeny.nex")

# Create some random dstate data
states <- sample(seq(1,40,1), 17)
names(states) <- phy$tip.label

head(states)

# Load the function code
source("color.terminal.branches.R")

```

A starting point plot

```{r}
color.terminal.branches(phy, states, breaks=4, cols=c("black","red"), edge.width=2, show.tip.label=TRUE)

```

Using three colors, partitioning the data finer

```{r}
color.terminal.branches(phy, states, breaks=8, cols=c("black","green","red"), edge.width=2)
```

If you wanted to make the non-terminal branches less obvious

```{r}
color.terminal.branches(phy, states, breaks=8, cols=c("black","green","red"), edge.width=2,non.terminal.col = "gray")

```
