calculate.ellipse.area - Calculate the size of morphological space occupied by taxa from multivariate morphological data
========================================================

This function calculates the amount of morphological space occupied by taxa based on the first two principle components from a principle component analysis

The function code can be downloaded here

```{r, quiet=T}
library(pracma)
library(car)

## ggbiplot is used for visualizing the data
library(ggbiplot)
```

Load the data, and load the functions
```{r}
dat <- read.csv("test.data.csv")

head(dat)

source("calculate.ellipse.area.R")
```

First we will do a manual analysis for visualization using ggbiplot. This is useful to make sure that the results returned agree visually with the data

```{r}
# Group information from our data
grp <- dat$Subspecies
pca1 <- prcomp(dat[,-1],scale=TRUE)
g <- ggbiplot(pca1, obs.scale = 1, var.scale = 1, 
              groups = grp, ellipse = TRUE, circle = FALSE)
g <- g + theme(legend.direction = 'horizontal', 
              legend.position = 'top')
g <- g + coord_fixed(ratio = 1.5)
g <- g +geom_point(size=1, aes(colour = grp))
print(g)
```

Now we can fun the main function to calculate the volume of each ellipse The function takes the following arguments:
```
* morpho.data: A `data.frame` of the morphological characters for each species
* group.info: A `factor` specifying what group each row in the `data.frame` belongs to
* conf.interval: What confidence interval to calculate the ellipses at
* scale.pca: Logical, should the principal components analysis scale the measurements before calculating the priniple components?
```

```{r}
# Group information from our data
grp <- dat$Subspecies

results <- calculate.morpho.poly.area(dat[,-1], group.info=grp, conf.interval=0.9, scale.pca =TRUE)

results
```

