Add HPD Info - Add probability density information into phylogenies
========================================================
This function is a precursor for the `HPDbars` function in the package `phyloch`. The function will, given a phylogeny and node information, combine the data which can then be passed to the `HPDbars` function. The aim here is to show the results at a selection of nodes, rather than all the nodes in the phylogeny.

This function requires that the package `phyloch` package be loaded.
```{r}
library(phyloch)
```

First we must load the file containing the function to be used, and load the example phylogeny.
```{r}
source("add_HPD_info.R")
phy <- read.nexus("example.phylo.nex")
```

Next, we will generate some data to be plotted onto our phylogeny:
```{r}
# This function requires that "node", "min" and "max" appear in the column names in some form
node_ages <- as.data.frame(matrix(NA, ncol=3, nrow=3))
colnames(node_ages) <- c("node", "Minimum", "Maximum")
node_ages[,1] <- c("23", "31", "29")
node_ages[,2] <- c(20, 17, 28)
node_ages[,3] <- c(35, 25, 35)

node_ages

```

Now we will run the function, creating a new object of class `phylo'
```{r}
phy.full <- add_HPD_info(phy, node_ages)
```

You can see the information that has been added in the following manner:
```{r}
str(phy.full)
```

This new phylogeny can then be passed to `HPDbars`. 

```{r }
plot(phy.full)
axisPhylo()
HPDbars(phy.full, col="darkblue", lwd=8)
```


