Make HPD node plot- Add probability density information into phylogenies
========================================================

_Updated Nov 2nd 2015: Function re-written to be much more stable, and added additional functionality_

The supporting files are the function code, phylogeny, and species group information.

There are two functions provided, with a few dependent packages:
```{r, quiet=T}
library(phyloch)
library(ape)
library(phytools)
library(strap)
```


First we must load the file containing the functions to be used, the example phylogeny, and the species group information.
```{r}
source("make_HPD_node_plot.R")
phy <- read.nexus("example.phylo.nex")
load("species_group_info.RData")
```

Next, we will generate some data to be plotted onto our phylogeny:
```{r}
# This function requires that "node", "min" and "max" appear in the column names in some form
age_data <- as.data.frame(matrix(NA, ncol=3, nrow=3))
colnames(age_data) <- c("Genus", "Minimum", "Maximum")
age_data[1,] <- c("Genus_A", 20 ,35 )
age_data[2,] <- c("Genus_B", 17, 28)
age_data[3,] <- c("Genus_C", 22, 35)

age_data[,2] <- as.numeric(age_data[,2])
age_data[,3] <- as.numeric(age_data[,3])

age_data

```

The first function provided (`find.nodes`) will identify the most recent common ancestor for each specified group. The nodes identified are where the age data will subsequently be plotted.

`find.nodes` requires:
```
* data: A `data.frame` containing the minimum, and and maximum ages, as well as the corresponding species group names
* phy: An object of class `phylo`
* spp_group_list: An object of class `list` where the names match the group names in `data`, and each element contains species found in `phy$tip.label`
* colname: A vector of class `character` and length 1. Specify the column name in `data` that correponds to the species group data
```

Using the previously defined age data, and loaded species group data:
```{r}
age.data.inc.nodes <- find.nodes(age_data, phy, species_group_info, colname = "Genus")
```

Now we have a `data.frame` with our age data, and the corresponding node in the phylogeny

```{r}
age.data.inc.nodes
```




The previously generated data can now be used to generate our plot:
```{r}
make_HPD_node_plot(phy=phy, data=age.data.inc.nodes, line.width=5, node.col = "lightblue",line.col = "red",node.pch=21, node.cex=2)
```

